---
title             : "Ambiguous Words"
shorttitle        : "AMBIGUOUS WORDS"

author: 
  - name          : "Nicholas R. Harp"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "nharp@huskers.unl.edu"
  - name          : "Catherine C. Brown"
    affiliation   : "1"
  - name          : "Maital Neta"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Nebraska-Lincoln"

authornote: |
  Nicholas R. Harp, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln
  Catherine C. Brown, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln
  Maital Neta, Department of Psychology, Center for Brain, Biology, and Behavior, University of Nebraska-Lincoln

abstract: |
  We found some ambiugous words.
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "ambiguity"
wordcount         : "X"

bibliography      : ["CANLab_UNL.bib"] 

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Set root directory
knitr::opts_knit$set(root.dir = '~/Documents/GitHub/Words/')

### load necessary libraries ###
library(readxl)
library(tidyverse)
library(openxlsx)
library(Rmisc)
library(broom)

source("data_cleaning_nh.R")
```
# Introduction
We wanted to identify ambiguous words. 

# Study 1: Pilot 

## Methods

### Participants
Workers on Amazon's Mchanical Turk (MTurk) were invted to participate in an eligibility screener worth \$0.20 with the option to earn a bonus of \$2.05 if they met the requirements and completed the entire study. See **Supplementary Information** for specific MTurk batch settings. The Workers clicked a hyperlink that directed them to the study. The screener task included demographic questions and one block of word ratings that included 5 instances of the word "negative" and 5 instances of the word "positive" (see Procedure below for full details). Workers were invited to complete the entire study if they indicated that they were over 18 years old, had English as their native language, had no history of psychological or neurological disorder, and correctly rated the words "positive" and "negative" as positive or negative with at least 80% accuracy. Of the 145 Workers who completed the screener, `r length(participants)` met the eligibility requirements, and `r length(final.participants)` (`r sum(str_count(demog$sex, "Female"))/length(final.participant) *100`% female, `r sum(str_count(demog$sex, "Male"))/length(final.participant) *100`% male) chose to complete the entire study. The final sample was `r sum(str_count(demog$race, "Asian"))/length(final.participant) *100`% Asian, `r sum(str_count(demog$race, "Black - not of Hispanic Origin"))/length(final.participant) *100`% Black, `r sum(str_count(demog$race, "White - not of Hispanic Origin"))/length(final.participant) *100`% White, with a mean(sd) age of `r mean(demog$age)`(`r sd(demog$age)`).

### Material

#### Stimuli


#### Software
All tasks were created and presented using Gorilla Experiment Builder [@anwyl-irvine_gorilla_2019].

### Procedure
#### Screener task
#### Word rating rask

### Data analysis

## Results

### Subjective ratings

### Reaction times

# Study 2: Comparison of words with valence bias and IPANAT

## Methods

### Participants

### Material

#### Stimuli
##### Valence Bias with Words
##### Valence Bias with Faces
##### Valence Bias with IAPS
##### IPANAT

#### Software

### Procedure
#### Valence Bias Tasks
#### IPANAT

### Data analysis
#### Valence Bias Tasks
#### IPANAT

## Results

### Subjective ratings
##### Valence Bias with Words
##### Valence Bias with Faces
##### Valence Bias with IAPS
##### IPANAT

### Reaction times
##### Valence Bias with Words
##### Valence Bias with Faces
##### Valence Bias with IAPS
##### IPANAT

### Relationships between the measures

# Discussion
We did this study.

\newpage

# References
```{r create_r-references}
r_refs(file = "CANLab_UNL.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

\newpage

# Supplementary Information
## MTurk Project Settings
The following are the settings used for the first batch on MTurk. This batch only contributed 6 respondents because the batch was published before the Gorilla task was fully functioning, and the batch expired before all HITs could be filled.

* Title: Screener: Rate words as positive or negative (WARNING: This HIT may contain adult content. Worker discretion is advised.)  
* Description: Bonus available ($2.05) to those who meet eligibility. Complete short demographic questions. Use your keyboard to indicate if you think individual words are positive or negative. 
* Keywords: survey, demographics, rating, rate, words 
* Reward per response: $0.2 
* Number of respondents: 9 
* Time allotted per worker: 1 Hour 
* Survey expires in: 7 Days 
* Auto-approve and pay Workers in: 3 Days 
* Require that Workers be Masters to do your tasks: Yes 
* Specify any additional qualifications Workers must meet to work on your tasks: 
    + Location is UNITED STATES (US) 
    + HIT Approval Rate (%) for all Requesters' HITs greater than 95 
    + Number of HITs Approved greater than 5000 
* Project contains adult content: selected 
* Task Visibility: Hidden - Only Workers that meet my Qualification requirements can see and preview my tasks 

The same settings were used for the rest of the batches except that they did not require that Workers be Masters and the Number of HITs Approved was set to greater than 500, not 5000.
